%-----------EXPERIENCE-----------%
\section{Experience}
\resumeSubHeadingListStart

    \resumeSubheading
    {Banco Falabella}{Apr 2019 -- today}
    {Software Engineer}{Santiago, Chile}
    \resumeItemListStart
        \resumeItem{Support in migration of service infrastructure, allowing agility in the development of new functionalities.}
        \resumeItem{Designed and implemented microservices using Express and NestJS.}
        \resumeItem{Part of the cross tools and libraries team for use in microservices.}
        \resumeItem{\textbf{Technologies used:} Nodejs, Express, NestJS, Angular, Java, Kong API Gateway, Docker, Git.}
    \resumeItemListEnd
    
    \resumeSubheading
    {IQ Build}{Dec 2018 -- Mar 2019}
    {Backend Engineer}{Santiago, Chile}
    \resumeItemListStart
        \resumeItem{Improved the databases queries performance up to 15\% using bulks inserts in couchDB.}
        \resumeItem{Designed and implemented new functionalities in the backend services.}
        \resumeItem{\textbf{Technologies used:} Nodejs, Express, CouchDB, Git.}
    \resumeItemListEnd

    \resumeSubheading
    {Everis Chile}{Jun 2017 -- Dec 2018}
    {Programmer}{Santiago, Chile}
    \resumeItemListStart
        \resumeItem{Developed frontend and backend modules for the largest project for the MDS client in 2017.}
        \resumeItem{Developed frontend and BFF services for the enterprise platform for BCI Bank (largest project for Everis Chile in 2018).}
        \resumeItem{\textbf{Technologies used:} PHP, Laravel, Nodejs, Express, Angular, SVN, Git.}
    \resumeItemListEnd

    \resumeSubheading
    {AIRA Virtual}{Feb 2017 -- Jun 2017}
    {Software Engineer}{Santiago, Chile}
    \resumeItemListStart
        \resumeItem{Designed and developed internal management tools.}
        \resumeItem{Developed frontend and backend services for the platform.}
        \resumeItem{\textbf{Technologies used:} PHP, Laravel, Vue, Materializecss, MySQL, Docker, Git.}
    \resumeItemListEnd

    \resumeSubheading
    {Everis Chile}{Sep 2015 -- Feb 2017}
    {Programmer}{Santiago, Chile}
    \resumeItemListStart
        \resumeItem{Led a technical team in the largest project for MDS client in 2015.}
        \resumeItem{Teached the Laravel framework to different teams for use in projects for MDS cliente.}
        \resumeItem{\textbf{Technologies used:} PHP, Laravel, Javascript, JQuery, Bootstrap, PLSQL, Oracle Database, SVN.}
    \resumeItemListEnd

    \resumeSubheading
    {CrowdTransfer}{Jul 2014 -- Sep 2015}
    {Software Engineer}{Santiago, Chile}
    \resumeItemListStart
        \resumeItem{Designed and implemented the first web version for an platform to connect people to send money abroad.}
        \resumeItem{Designed the Database model and architecture for the platform.}
        \resumeItem{\textbf{Technologies used:} PHP, Laravel, AngularJS, Swift 1, Bootstrap, MySQL, Heroku, Git.}
    \resumeItemListEnd

\resumeSubHeadingListEnd
